Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-02 WSSSPE3/report/wg_appendix_user_community.tex
Create wg_appendix_user_community.tex
Former-commit-id: 5c55415aa3f0501218576f3184eab289d523ff83
Reformatted group members to itemized list to ensure they appear in the right place.
Former-commit-id: e4584de998d67127bdd327661163fca316f83c01
adding POC request to appendices
Former-commit-id: 42aa40a42eb82bf40df6e482de5fb48dc9085b8d

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Industry Interaction Working Group Discussion}
\label{sec:appendix_industry_interaction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Group Members}
{\small
\begin{longtable}{ll}
   name            &  affiliation
\\ name2           &  affiliation2
\end{longtable}
}

@@

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{User Community Working Group Discussion}
\label{sec:appendix_user_community}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{add POC here}

\subsection{Group Members}

\begin{itemize}
\item Ethan Davis -- UCAR Unidata
\item Dan Gunter -- Lawrence Berkeley National Lab
\item Liz Jessup -- University of Colorado
\item Mark Miller -- University of California, San Diego
\item Lindsey Powers -- The HDF Group
\item Daniel Ziskin -- NCAR Atmospheric Chemistry Observations and Modeling (ACOM) Laboratory
\end{itemize}

@@

The main opportunity is to increase awareness among scientific
software developers and project managers of the importance of
developing a community around their project.
While this message is fairly well understood in the open source
community, the scientific community can be more focused on the
science a software project is supporting rather than the software
project itself.

As with many of the issues relevant to the sustainability of science
software, the main challenge here will be changing the culture and
expectations around scientific software.

@@

\begin{itemize}
\item Survey successful science software projects
\item Survey community members from the surveyed projects
\item Distill the survey results and document best practices around community engagement
\item Look for ways to raise awareness
\end{itemize}
